Manuscript figures

### 2024-12-05 Manuscript_figures.Rmd
Updated manuscript figures

# Perform a paired ANOVA separately for each gender
anova_res_F <- aov(count ~ visit + Error(patient/visit), data = gene_counts_long %>% filter(sex == "F"))
anova_res_M <- aov(count ~ visit + Error(patient/visit), data = gene_counts_long %>% filter(sex == "M"))

# Extract ANOVA p-values
anova_pval_F <- summary(anova_res_F)[[2]][[1]][["Pr(>F)"]][1]
anova_pval_M <- summary(anova_res_M)[[2]][[1]][["Pr(>F)"]][1]

# Perform paired Wilcoxon tests for each sex
wilcox_res <- list(
  visit1_vs_visit2_F = wilcox.test(
    x = gene_counts_long %>% filter(visit == "visit_1", sex == "F") %>% pull(count),
    y = gene_counts_long %>% filter(visit == "visit_2", sex == "F") %>% pull(count),
    paired = TRUE
  ),
  visit1_vs_visit3_F = wilcox.test(
    x = gene_counts_long %>% filter(visit == "visit_1", sex == "F") %>% pull(count),
    y = gene_counts_long %>% filter(visit == "visit_3", sex == "F") %>% pull(count),
    paired = TRUE
  ),
  visit2_vs_visit3_F = wilcox.test(
    x = gene_counts_long %>% filter(visit == "visit_2", sex == "F") %>% pull(count),
    y = gene_counts_long %>% filter(visit == "visit_3", sex == "F") %>% pull(count),
    paired = TRUE
  ),
  visit1_vs_visit2_M = wilcox.test(
    x = gene_counts_long %>% filter(visit == "visit_1", sex == "M") %>% pull(count),
    y = gene_counts_long %>% filter(visit == "visit_2", sex == "M") %>% pull(count),
    paired = TRUE
  ),
  visit1_vs_visit3_M = wilcox.test(
    x = gene_counts_long %>% filter(visit == "visit_1", sex == "M") %>% pull(count),
    y = gene_counts_long %>% filter(visit == "visit_3", sex == "M") %>% pull(count),
    paired = TRUE
  ),
  visit2_vs_visit3_M = wilcox.test(
    x = gene_counts_long %>% filter(visit == "visit_2", sex == "M") %>% pull(count),
    y = gene_counts_long %>% filter(visit == "visit_3", sex == "M") %>% pull(count),
    paired = TRUE
  )
)

wilcox_pvals <- sapply(wilcox_res, function(x) x$p.value)

# Create the boxplot with significance annotations
plot <- ggplot(gene_counts_long, aes(x = interaction(visit, sex), y = count, fill = visit)) +
  geom_boxplot(outlier.shape = NA) +  # Remove outliers
  geom_jitter(color = "grey", size = 1, width = 0.2, alpha = 0.5) +  # Add individual points
  #geom_line(aes(group = Patient), color = "grey", size = 0.3, linetype = "solid", alpha = 0.6) +  # Connect paired values with thin lines
  labs(title = gene_of_interest, x = "Visit and Sex", y = "Gene Count") +
  theme_minimal() +
  geom_signif(
    comparisons = list(
      c("visit_1.F", "visit_2.F"), 
      c("visit_1.F", "visit_3.F"), 
      c("visit_2.F", "visit_3.F"),
      c("visit_1.M", "visit_2.M"), 
      c("visit_1.M", "visit_3.M"), 
      c("visit_2.M", "visit_3.M")
    ),
    map_signif_level = TRUE,
    test = "wilcox.test",
    test.args = list(paired = TRUE)
  ) +
  theme(plot.title = element_text(size = 10))

# Add ANOVA p-values to the plot
plot <- plot + annotate("text", x = 1, y = max(gene_counts_long$count), label = paste("ANOVA F p-value:", format(anova_pval_F, digits = 3)), hjust = 0, vjust = 1, size = 3)
plot <- plot + annotate("text", x = 4, y = max(gene_counts_long$count), label = paste("ANOVA M p-value:", format(anova_pval_M, digits = 3)), hjust = 0, vjust = 1, size = 3)

@@

    # Wilcoxon
    stat.test <- plot.dat %>%
      group_by(bin, sex) %>%
      wilcox_test(mm~sex_visit, paired = T)

@@

    pp
  }) %>% 
  cowplot::plot_grid(plotlist = ., ncol = 3)
```

@@

We provide lists with filtered count matrices per visit.

@@

```{r s1a, fig.width=8, fig.height=4}
cms %>% 
  lapply(\(x) diff(x@p)) %>% 
  sapply(median) %>% 
  {data.frame(sample = names(.), 
              value = unname(.))} %>% 
  mutate(visit = strsplit(sample, "_") %>% 
           sget(3)) %>% 
  mutate(sample = paste0("Donor", seq(14), "_", visit) %>% 
           factor(., levels = unique(.))) %>% 
  ggplot(aes(sample, value, fill = visit)) +
  geom_col() +
  theme_bw() +
  theme(line = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  labs(x = "", y = "Median genes", fill = "") +
  scale_fill_manual(values = ggsci::pal_jama()(3))
```

```{r s1a2}
cms %>% 
  lapply(sparseMatrixStats::colSums2) %>% 
  sapply(median) %>% 
  {data.frame(sample = names(.), 
              value = unname(.))} %>% 
  mutate(visit = strsplit(sample, "_") %>% 
           sget(3)) %>% 
  mutate(sample = paste0("Donor", seq(14), "_", visit) %>% 
           factor(., levels = unique(.))) %>% 
  ggplot(aes(sample, value, fill = visit)) +
  geom_col() +
  theme_bw() +
  theme(line = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  labs(x = "", y = "Median UMIs", fill = "") +
  scale_fill_manual(values = ggsci::pal_jama()(3))
```

@@

@@

```{r s3c}
varToPlot <- spc %>% 
  as.character() %>% 
  strsplit("_vis") %>% 
  sget(1) %>% 
  setNames(names(spc)) %>% 
  factor(labels = paste0("Donor", seq(14))) %>% 
  .[names(.) %in% names(anno.lymphoid)]

con$plotGraph(groups = varToPlot, 
              plot.na = F, 
              size = 0.5,
              alpha = 0.8, 
              embedding = "largeVis",
              mark.groups = F,
              show.labels = T,
              show.legend = T,
              title = "Donor") +
  labs(x = "largeVis1", y = "largeVis2", col = "") + 
  theme(line = element_blank()) +
  dotSize(3)
```

>>>>

# Define a helper function to map p-values to stars
pval_to_stars <- function(p) {
  if (p < 0.0001) {
    return("****")
  } else if (p < 0.001) {
    return("***")
  } else if (p < 0.01) {
    return("**")
  } else if (p < 0.05) {
    return("*")
  } else {
    return("ns")  # Not significant
  }
}

# Perform a Kruskal-Wallis test separately for each gender
kw_res_F <- kruskal.test(count ~ visit, data = gene_counts_long %>% filter(sex == "F"))
kw_res_M <- kruskal.test(count ~ visit, data = gene_counts_long %>% filter(sex == "M"))

# Extract Kruskal-Wallis p-values
kw_pval_F <- kw_res_F$p.value
kw_pval_M <- kw_res_M$p.value

# Perform paired Wilcoxon tests for each gender with Holm's correction
paired_wilcox <- function(data, sex_group) {
  data_sex <- data %>% filter(sex == sex_group)
  pairwise_tests <- list(
    visit1_vs_visit2 = wilcox.test(
      x = data_sex %>% filter(visit == "visit_1") %>% pull(count),
      y = data_sex %>% filter(visit == "visit_2") %>% pull(count),
      paired = TRUE
    )$p.value,
    visit1_vs_visit3 = wilcox.test(
      x = data_sex %>% filter(visit == "visit_1") %>% pull(count),
      y = data_sex %>% filter(visit == "visit_3") %>% pull(count),
      paired = TRUE
    )$p.value,
    visit2_vs_visit3 = wilcox.test(
      x = data_sex %>% filter(visit == "visit_2") %>% pull(count),
      y = data_sex %>% filter(visit == "visit_3") %>% pull(count),
      paired = TRUE
    )$p.value
  )
  corrected_pvals <- p.adjust(unlist(pairwise_tests), method = "holm")
  return(corrected_pvals)
}

wilcox_pvals_F <- paired_wilcox(gene_counts_long, "F")
wilcox_pvals_M <- paired_wilcox(gene_counts_long, "M")

# Map the Wilcoxon p-values to stars
wilcox_stars_F <- sapply(wilcox_pvals_F, pval_to_stars)
wilcox_stars_M <- sapply(wilcox_pvals_M, pval_to_stars)

# Create the boxplot with significance annotations
plot <- ggplot(gene_counts_long, aes(x = interaction(visit, sex), y = count, fill = visit)) +
  geom_boxplot(outlier.shape = NA) +  # Remove outliers
  geom_jitter(color = "grey", size = 1, width = 0.2, alpha = 0.5) +  # Add individual points
  labs(title = "Gene Expression Across Visits and Genders", x = "Visit and Sex", y = "Gene Count") +
  theme_minimal() +
  theme(plot.title = element_text(size = 10)) +
  geom_signif(
    comparisons = list(
      c("visit_1.F", "visit_2.F"), 
      c("visit_1.F", "visit_3.F"), 
      c("visit_2.F", "visit_3.F"),
      c("visit_1.M", "visit_2.M"), 
      c("visit_1.M", "visit_3.M"), 
      c("visit_2.M", "visit_3.M")
    ),
    annotations = c(
      wilcox_stars_F["visit1_vs_visit2"],
      wilcox_stars_F["visit1_vs_visit3"],
      wilcox_stars_F["visit2_vs_visit3"],
      wilcox_stars_M["visit1_vs_visit2"],
      wilcox_stars_M["visit1_vs_visit3"],
      wilcox_stars_M["visit2_vs_visit3"]
    ),
    textsize = 4,
    map_signif_level = FALSE
  )

# Add Kruskal-Wallis p-values as text
plot <- plot + 
  annotate("text", x = 1, y = max(gene_counts_long$count) * 1.1, 
           label = paste("KW Female p-value:", format(kw_pval_F, digits = 3)), 
           hjust = 0, size = 3) +
  annotate("text", x = 4, y = max(gene_counts_long$count) * 1.1, 
           label = paste("KW Male p-value:", format(kw_pval_M, digits = 3)), 
           hjust = 0, size = 3)

@@

    # Wilcoxon
    stat.test <- plot.dat %>%
      group_by(bin, sex) %>%
      wilcox_test(mm~sex_visit, paired = F)

@@

    pp
  }) %>% 
  cowplot::plot_grid(plotlist = ., ncol = 3) -> p
```

@@

@@

```{r s1a, fig.width=8, fig.height=4}
cms %>% 
  lapply(\(x) diff(x@p)) %>% 
  sapply(median) %>% 
  {data.frame(sample = names(.),
              value = unname(.))} %>% 
  mutate(visit = strsplit(sample, "_") %>% 
           sget(3)) %>% 
  mutate(sample = factor(sample, levels = sample)) %>%
  ggplot(aes(sample, value, fill = visit)) +
  geom_col() +
  theme_bw() +
  theme(line = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  labs(x = "", y = "Median genes", fill = "") +
  scale_fill_manual(values = ggsci::pal_jama()(3))
```

```{r s1a2}
cms %>% 
  lapply(sparseMatrixStats::colSums2) %>% 
  sapply(median) %>% 
  {data.frame(sample = names(.), 
              value = unname(.))} %>% 
  mutate(visit = strsplit(sample, "_") %>% 
           sget(3)) %>% 
  mutate(sample = factor(sample, levels = sample)) %>%
  ggplot(aes(sample, value, fill = visit)) +
  geom_col() +
  theme_bw() +
  theme(line = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  labs(x = "", y = "Median UMIs", fill = "") +
  scale_fill_manual(values = ggsci::pal_jama()(3))
```

@@

## Figure S3A

```{r, fs3a}
## Plot Individual genes from RNA-seq data
Bulk_norm_counts <- read.delim("Bulk_norm_counts.txt", h=T)
colData <- read.delim("Meta_Data_WL_Select.txt", h=T, dec = ",")
```

```{r}
gene_of_interest <- "TNF"

# Define a helper function to map p-values to stars
pval_to_stars <- function(p) {
  if (p < 0.0001) {
    return("****")
  } else if (p < 0.001) {
    return("***")
  } else if (p < 0.01) {
    return("**")
  } else if (p < 0.05) {
    return("*")
  } else {
    return("ns")  # Not significant
  }
}

# Perform a Kruskal-Wallis test separately for each gender
kw_res_F <- kruskal.test(count ~ visit, data = gene_counts_long %>% filter(sex == "F"))
kw_res_M <- kruskal.test(count ~ visit, data = gene_counts_long %>% filter(sex == "M"))

# Extract Kruskal-Wallis p-values
kw_pval_F <- kw_res_F$p.value
kw_pval_M <- kw_res_M$p.value

# Perform paired Wilcoxon tests for each gender with Holm's correction
paired_wilcox <- function(data, sex_group) {
  data_sex <- data %>% filter(sex == sex_group)
  pairwise_tests <- list(
    visit1_vs_visit2 = wilcox.test(
      x = data_sex %>% filter(visit == "visit_1") %>% pull(count),
      y = data_sex %>% filter(visit == "visit_2") %>% pull(count),
      paired = TRUE
    )$p.value,
    visit1_vs_visit3 = wilcox.test(
      x = data_sex %>% filter(visit == "visit_1") %>% pull(count),
      y = data_sex %>% filter(visit == "visit_3") %>% pull(count),
      paired = TRUE
    )$p.value,
    visit2_vs_visit3 = wilcox.test(
      x = data_sex %>% filter(visit == "visit_2") %>% pull(count),
      y = data_sex %>% filter(visit == "visit_3") %>% pull(count),
      paired = TRUE
    )$p.value
  )
  corrected_pvals <- p.adjust(unlist(pairwise_tests), method = "holm")
  return(corrected_pvals)
}

wilcox_pvals_F <- paired_wilcox(gene_counts_long, "F")
wilcox_pvals_M <- paired_wilcox(gene_counts_long, "M")

# Map the Wilcoxon p-values to stars
wilcox_stars_F <- sapply(wilcox_pvals_F, pval_to_stars)
wilcox_stars_M <- sapply(wilcox_pvals_M, pval_to_stars)

# Create the boxplot with significance annotations
plot <- ggplot(gene_counts_long, aes(x = interaction(visit, sex), y = count, fill = visit)) +
  geom_boxplot(outlier.shape = NA) +  # Remove outliers
  geom_jitter(color = "grey", size = 1, width = 0.2, alpha = 0.5) +  # Add individual points
  labs(title = "Gene Expression Across Visits and Genders", x = "Visit and Sex", y = "Gene Count") +
  theme_minimal() +
  theme(plot.title = element_text(size = 10)) +
  geom_signif(
    comparisons = list(
      c("visit_1.F", "visit_2.F"), 
      c("visit_1.F", "visit_3.F"), 
      c("visit_2.F", "visit_3.F"),
      c("visit_1.M", "visit_2.M"), 
      c("visit_1.M", "visit_3.M"), 
      c("visit_2.M", "visit_3.M")
    ),
    annotations = c(
      wilcox_stars_F["visit1_vs_visit2"],
      wilcox_stars_F["visit1_vs_visit3"],
      wilcox_stars_F["visit2_vs_visit3"],
      wilcox_stars_M["visit1_vs_visit2"],
      wilcox_stars_M["visit1_vs_visit3"],
      wilcox_stars_M["visit2_vs_visit3"]
    ),
    textsize = 4,
    map_signif_level = FALSE
  )

# Add Kruskal-Wallis p-values as text
plot <- plot + 
  annotate("text", x = 1, y = max(gene_counts_long$count) * 1.1, 
           label = paste("KW Female p-value:", format(kw_pval_F, digits = 3)), 
           hjust = 0, size = 3) +
  annotate("text", x = 4, y = max(gene_counts_long$count) * 1.1, 
           label = paste("KW Male p-value:", format(kw_pval_M, digits = 3)), 
           hjust = 0, size = 3)

```{r}
gene_of_interest <- "CCL3"

# Define a helper function to map p-values to stars
pval_to_stars <- function(p) {
  if (p < 0.0001) {
    return("****")
  } else if (p < 0.001) {
    return("***")
  } else if (p < 0.01) {
    return("**")
  } else if (p < 0.05) {
    return("*")
  } else {
    return("ns")  # Not significant
  }
}

# Perform a Kruskal-Wallis test separately for each gender
kw_res_F <- kruskal.test(count ~ visit, data = gene_counts_long %>% filter(sex == "F"))
kw_res_M <- kruskal.test(count ~ visit, data = gene_counts_long %>% filter(sex == "M"))

# Extract Kruskal-Wallis p-values
kw_pval_F <- kw_res_F$p.value
kw_pval_M <- kw_res_M$p.value

# Perform paired Wilcoxon tests for each gender with Holm's correction
paired_wilcox <- function(data, sex_group) {
  data_sex <- data %>% filter(sex == sex_group)
  pairwise_tests <- list(
    visit1_vs_visit2 = wilcox.test(
      x = data_sex %>% filter(visit == "visit_1") %>% pull(count),
      y = data_sex %>% filter(visit == "visit_2") %>% pull(count),
      paired = TRUE
    )$p.value,
    visit1_vs_visit3 = wilcox.test(
      x = data_sex %>% filter(visit == "visit_1") %>% pull(count),
      y = data_sex %>% filter(visit == "visit_3") %>% pull(count),
      paired = TRUE
    )$p.value,
    visit2_vs_visit3 = wilcox.test(
      x = data_sex %>% filter(visit == "visit_2") %>% pull(count),
      y = data_sex %>% filter(visit == "visit_3") %>% pull(count),
      paired = TRUE
    )$p.value
  )
  corrected_pvals <- p.adjust(unlist(pairwise_tests), method = "holm")
  return(corrected_pvals)
}

wilcox_pvals_F <- paired_wilcox(gene_counts_long, "F")
wilcox_pvals_M <- paired_wilcox(gene_counts_long, "M")

# Map the Wilcoxon p-values to stars
wilcox_stars_F <- sapply(wilcox_pvals_F, pval_to_stars)
wilcox_stars_M <- sapply(wilcox_pvals_M, pval_to_stars)

# Create the boxplot with significance annotations
plot <- ggplot(gene_counts_long, aes(x = interaction(visit, sex), y = count, fill = visit)) +
  geom_boxplot(outlier.shape = NA) +  # Remove outliers
  geom_jitter(color = "grey", size = 1, width = 0.2, alpha = 0.5) +  # Add individual points
  labs(title = "Gene Expression Across Visits and Genders", x = "Visit and Sex", y = "Gene Count") +
  theme_minimal() +
  theme(plot.title = element_text(size = 10)) +
  geom_signif(
    comparisons = list(
      c("visit_1.F", "visit_2.F"), 
      c("visit_1.F", "visit_3.F"), 
      c("visit_2.F", "visit_3.F"),
      c("visit_1.M", "visit_2.M"), 
      c("visit_1.M", "visit_3.M"), 
      c("visit_2.M", "visit_3.M")
    ),
    annotations = c(
      wilcox_stars_F["visit1_vs_visit2"],
      wilcox_stars_F["visit1_vs_visit3"],
      wilcox_stars_F["visit2_vs_visit3"],
      wilcox_stars_M["visit1_vs_visit2"],
      wilcox_stars_M["visit1_vs_visit3"],
      wilcox_stars_M["visit2_vs_visit3"]
    ),
    textsize = 4,
    map_signif_level = FALSE
  )

# Add Kruskal-Wallis p-values as text
plot <- plot + 
  annotate("text", x = 1, y = max(gene_counts_long$count) * 1.1, 
           label = paste("KW Female p-value:", format(kw_pval_F, digits = 3)), 
           hjust = 0, size = 3) +
  annotate("text", x = 4, y = max(gene_counts_long$count) * 1.1, 
           label = paste("KW Male p-value:", format(kw_pval_M, digits = 3)), 
           hjust = 0, size = 3)

```{r}
gene_of_interest <- "CCL5"

# Define a helper function to map p-values to stars
pval_to_stars <- function(p) {
  if (p < 0.0001) {
    return("****")
  } else if (p < 0.001) {
    return("***")
  } else if (p < 0.01) {
    return("**")
  } else if (p < 0.05) {
    return("*")
  } else {
    return("ns")  # Not significant
  }
}

# Perform a Kruskal-Wallis test separately for each gender
kw_res_F <- kruskal.test(count ~ visit, data = gene_counts_long %>% filter(sex == "F"))
kw_res_M <- kruskal.test(count ~ visit, data = gene_counts_long %>% filter(sex == "M"))

# Extract Kruskal-Wallis p-values
kw_pval_F <- kw_res_F$p.value
kw_pval_M <- kw_res_M$p.value

# Perform paired Wilcoxon tests for each gender with Holm's correction
paired_wilcox <- function(data, sex_group) {
  data_sex <- data %>% filter(sex == sex_group)
  pairwise_tests <- list(
    visit1_vs_visit2 = wilcox.test(
      x = data_sex %>% filter(visit == "visit_1") %>% pull(count),
      y = data_sex %>% filter(visit == "visit_2") %>% pull(count),
      paired = TRUE
    )$p.value,
    visit1_vs_visit3 = wilcox.test(
      x = data_sex %>% filter(visit == "visit_1") %>% pull(count),
      y = data_sex %>% filter(visit == "visit_3") %>% pull(count),
      paired = TRUE
    )$p.value,
    visit2_vs_visit3 = wilcox.test(
      x = data_sex %>% filter(visit == "visit_2") %>% pull(count),
      y = data_sex %>% filter(visit == "visit_3") %>% pull(count),
      paired = TRUE
    )$p.value
  )
  corrected_pvals <- p.adjust(unlist(pairwise_tests), method = "holm")
  return(corrected_pvals)
}

wilcox_pvals_F <- paired_wilcox(gene_counts_long, "F")
wilcox_pvals_M <- paired_wilcox(gene_counts_long, "M")

# Map the Wilcoxon p-values to stars
wilcox_stars_F <- sapply(wilcox_pvals_F, pval_to_stars)
wilcox_stars_M <- sapply(wilcox_pvals_M, pval_to_stars)

# Create the boxplot with significance annotations
plot <- ggplot(gene_counts_long, aes(x = interaction(visit, sex), y = count, fill = visit)) +
  geom_boxplot(outlier.shape = NA) +  # Remove outliers
  geom_jitter(color = "grey", size = 1, width = 0.2, alpha = 0.5) +  # Add individual points
  labs(title = "Gene Expression Across Visits and Genders", x = "Visit and Sex", y = "Gene Count") +
  theme_minimal() +
  theme(plot.title = element_text(size = 10)) +
  geom_signif(
    comparisons = list(
      c("visit_1.F", "visit_2.F"), 
      c("visit_1.F", "visit_3.F"), 
      c("visit_2.F", "visit_3.F"),
      c("visit_1.M", "visit_2.M"), 
      c("visit_1.M", "visit_3.M"), 
      c("visit_2.M", "visit_3.M")
    ),
    annotations = c(
      wilcox_stars_F["visit1_vs_visit2"],
      wilcox_stars_F["visit1_vs_visit3"],
      wilcox_stars_F["visit2_vs_visit3"],
      wilcox_stars_M["visit1_vs_visit2"],
      wilcox_stars_M["visit1_vs_visit3"],
      wilcox_stars_M["visit2_vs_visit3"]
    ),
    textsize = 4,
    map_signif_level = FALSE
  )

# Add Kruskal-Wallis p-values as text
plot <- plot + 
  annotate("text", x = 1, y = max(gene_counts_long$count) * 1.1, 
           label = paste("KW Female p-value:", format(kw_pval_F, digits = 3)), 
           hjust = 0, size = 3) +
  annotate("text", x = 4, y = max(gene_counts_long$count) * 1.1, 
           label = paste("KW Male p-value:", format(kw_pval_M, digits = 3)), 
           hjust = 0, size = 3)

@@

```{r s3c, fig.width=7, fig.height=4}
pdf("/work/02_data/00_prints/S3A.pdf", width = 7, height = 4)
varToPlot <- spc %>% 
  as.character() %>% 
  strsplit("_vis") %>% 
  sget(1) %>% 
  setNames(names(spc)) %>%
  .[names(.) %in% names(anno.lymphoid)]

con$plotGraph(groups = varToPlot, 
              plot.na = F, 
              size = 0.5,
              alpha = 0.8, 
              embedding = "largeVis",
              mark.groups = F,
              show.labels = T,
              show.legend = T,
              title = "Donor") +
  labs(x = "largeVis1", y = "largeVis2", col = "") + 
  theme(line = element_blank()) +
  dotSize(3)
dev.off()
```
